NMRlipids IV: Other than PC headgroups

### 2017-02-22 Manuscript/manuscript.tex
Updates

Absolute values of experimental order parameters for different lipid headgroups are
collected in Fig. \ref{HGorderParameters}. Signs are measured only for PC as far as I know,
thus only absolute values are used for now.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparameters.eps}
  \caption{\label{HGorderParameters}
    Absolute values of order parameters for headgroup and glycerol backbone with different headgroups
    from experiments. POPC values are from \cite{ferreira13}, DOPS from \cite{browning80} contains 0.1M of NaCl,
    POPG from \cite{borle85} contains 10nM PIPES, DPPE from \cite{seelig76}, E.coliPE and E.coliPG are from \cite{gally81}.
  }
\end{figure}

@@

>>>>

Absolute values of experimental order parameters for different lipid headgroups are
collected in Fig. \ref{HGorderParameters}. Signs are measured only for PC as far as I know,
thus only absolute values are used for now.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparameters.eps}
  \caption{\label{HGorderParameters}
    Absolute values of order parameters for headgroup and glycerol backbone with different headgroups
    from experiments. POPC values are from \cite{ferreira13}, DOPS from \cite{browning80} contains 0.1M of NaCl,
    POPG from \cite{borle85} contains 10nM PIPES, DPPG from \cite{wohlgemuth80} contains  10mM PIPES and 100mM NaCl,
    DPPE from \cite{seelig76}, E.coliPE and E.coliPG are from \cite{gally81}.
  }
\end{figure}

@@

Glycerol backbone and headgroup order parameters for PS lipids from experiments
and simulations are shown in Fig. \ref{HGorderParametersPOPS}.
The preliminary test with CHARMM GUI simulations show suggest that the model
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPG.eps}
  \caption{\label{HGorderParametersPOPG}
    Order parameters for PG headgroup and glycerol backbone from simulations and experiments without CaCl$_2$ 
    (POPG from \cite{borle85} contains 10mM of PIPES, DPPG from \cite{wohlgemuth80} contains 10mM PIPES and 100mM CaCl,
    E.Coli PG results from \cite{gally81}).
    Absolute values are shown, because signs are not known for experimental data.
    Glycerol backbone order parameters are negative in simulations, while $alpha$, $\beta$ and
    smaller $\gamma$ are positive.
  }
  \todo{More simulation data for lipids with different headgroups to be collected}
  \todo{CHARMM GUI simulation contains only counter ions as potassium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.}
  \todo{Experimental signs of the order parameters would highly useful.}
\end{figure}
